A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer

### 2011-01-28 paper.tex
Fix Franck points

\begin{abstract}
The search for new simplified interaction techniques is always treated as a
manner to advance the communication with intelligent devices.
In this paper we present our work to generate intelligent TVs modules capable of
recognizing human gestures through a low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements to control a TV in an ubiquitous computing environment.
Then we present a new gesture library generated after an analysis of TV's Talk-shows.

@@

\section{Gesture Semantics}
First sources of gestures can come from the interaction between two human in a
discussion, these type of gestures are used to add more precision on the details
and they are made by the same mental region of the speech \cite{SymbolicGest}.

@@

\subsection{Gestures taxonomies}
By looking in the possible gestures human can generate\cite{Gesturecraft}, we
get a huge amount of possibilities so there is a need for a taxonomy.
Many possible taxonomies exist according to the technical or analytical aspects:
\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture use:] We use this technique to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
% \item[]
% \item[]
\end{description}

%Gesture and Thoughts, page 18
\begin{description}
 \item[Gesticulation] is motion that embodies a meaning relatable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

@@

The figure.\ref{handg} shows our supported gestures. We provide a movement mode
used to select directions, then a command mode, then a hand fingers recognition,
and in the end a cursor movement mode.

@@

\subsection{Color Manipulations}
The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
We do an histogram tuning to better enlarge the colors to all the space available.
Then we transform the color space from BGR to YCrCb because it’s the one with the less parameters where we can do easy segmentation. The transformation from these two color spaces is chosen also because it’s linear []

\begin{center}
\begin{tabular}{c|c|c|c|c}
\textbf{Space} & RGB & HSV & YCrCb & CIE Lab\\
  & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
  & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & &
\end{tabular}
\end{center}

\subsection{Input Filtering}
Then, a morphological kernel is applied to smooth the results, this is necessary to clean the image from lonely pixels and holes inside skin zones.
Each blob is labeled in linear time we use the algorithm [], which requires 1 to 4 passes to recognize all blobs with their bounding path.
We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.

@@

We have used four modes a first core with the possibility to add more sub-gestures in the future.
This core will be used to control a children game having to select, choose, and answer basic questions.
We have stick to that scenario to produce these gestures.

@@

>>>>

\begin{abstract}
The search for new simplified interaction techniques is always treated as a
manner to advance the communication with interactive devices.
In this paper we present our work to generate interactive TVs modules capable of
recognizing human gestures through a low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements to control a TV in an ubiquitous computing environment.
Then we present a new gesture library generated after an analysis of TV's Talk-shows.

@@

\section{Gesture Semantics}
First sources of gestures can come from the interaction between two human in a
discussion, these type of gestures are used to add more precision on the details
and they are made by the same auditory areas of the cortex \cite{SymbolicGest}.

@@

\subsection{Gestures taxonomies}
By looking in the possible gestures human can generate \cite{Gesturecraft}, we
get a huge amount of possibilities so there is a need for a taxonomy.
Many possible taxonomies exist according to the technical or analytical aspects:
\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
% \item[]
% \item[]
\end{description}
%Gesture and Thoughts, page 18
\begin{description}
 \item[Gesticulation] is motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

@@

The figure\ref{handg} shows our supported gestures. We provide a movement mode
used to select directions, then a command mode, then a hand fingers recognition,
and in the end a cursor movement mode.

@@

\subsection{Color Transformations}
The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
We do an histogram tuning to better enlarge the colors to all the space available.
Then we transform the color space from BGR to YCrCb because it’s the one with the less parameters where we can do easy segmentation. The transformation from these two color spaces is chosen also because it’s linear \cite{skinColorSeg}.

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\textbf{Space} & BGR & HSV & YCrCb & CIE Lab\\
  & R>95, G>40, B>20, & H[0.4 .. 0.7] & Cb[77 .. 127] & C[0 .. 65] \\
\textbf{Param.} & Max\{R,G,B\}-Min\{R,G,B\} < 15 & S[0.15 .. 0.75] & Cr[133 .. 173] & I[0 .. 14] \\
  & abs(R-G) > 15, R > G, R>B & V[0.35 .. 0.95] & &
\end{tabular}
\end{center}

\subsection{Input Filtering}
Then, a morphological kernel is applied to smooth the results, this is necessary
to clean the image from lonely pixels and holes inside skin zones.
Each blob is labeled in linear time we use the algorithm \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.

@@

We have used four modes in a first core with the possibility to add more sub-gestures in the future.
This core will be used to control a children game having to select, choose, and answer basic questions.
We have stick to that scenario to produce these gestures.

@@

\section{}
